### 2020-05-06 gas-adsorption/gas-ads-body.tex
multiple changes to introduction and added citations to gas-ads abstract.

% \jordan{I got the values from wikipedia but the citation that wikipedia gave didn't link to the correct paper? Article is Energy Density.
% THIS PAPER says H2 at 700 bar is 4.7 MJ/L: Review on processing of metal–organic framework (MOF) materials towards system integration for hydrogen storage
% }
At ambient conditions, both methane
%(0.036 MJ/L)
and hydrogen gas
%(0.01 MJ/L)
possess a very low volumetric energy density compared to (liquid) gasoline.
%(34.2 MJ/L)
Consequently, under storage space constraints in passenger vehicles, natural gas and hydrogen must be densified for onboard storage to achieve a reasonable driving range on a ``full'' tank of fuel. Traditional densification approaches are liquefaction (cryogenic storage near atmospheric pressure)
% (at 1 atm, liquid CH$_4$ at 111~K to achieve 22.2 MJ/L~\cite{makal2012methane}, liquid H$_2$ at 20 K to achieve 8~MJ/L \cite{suh2011hydrogen})
or compression to high pressures (room temperature storage).
% (200 bar for CH$_4$ to achieve 9.2 MJ/L \cite{makal2012methane} and 700 bar for H$_2$ to achieve 4.5-5.3 MJ/L~\cite{unknown}).
Both approaches require expensive infrastructure at refilling stations and significant energy input; e.g., liquefaction of hydrogen consumes at least 30\% of its energy content \cite{bossel2003energy}. Moreover, high-pressure storage tanks are heavy, thick-walled, and non-conformable, while cryogenic storage tanks are bulky, expensive, and afflicted by boil-off losses \cite{hasan2009minimizing}.
% \jordan{
% Both forms of densification suffer several drawbacks varying from safety issues,  excessively expensive, boil-off~\cite{hasan2009minimizing}, and extensive refilling infrastructure~\cite{bossel2003energy}. 
% }
% % Jordan: I commented this out! % Cory: I shorted it. I think it's important.

A promising approach to densify natural gas \cite{makal2012methane,mason2014evaluating} and hydrogen \cite{suh2011hydrogen,garcia2018benchmark} for vehicular storage is through physical adsorption in nanoporous materials at room temperature~\cite{schoedel2016role}. The internal surfaces of porous materials attract gas molecules through van der Waals, electrostatic, etc. interactions to achieve a higher adsorbed gas density than the bulk gas at the same temperature and pressure, allowing for room temperature and lower-pressure storage and alleviating many drawbacks of high-pressure storage.
% This would thereby reduce the cost of infrastructure at refilling stations, allow thinner-walled and therefore cheaper and lighter pressure vessels, reduce the energy requirements for gas densification, and alleviate safety concerns with high pressure storage.

@@

For a vehicle employing a porous material to store natural gas or hydrogen, the (volumetric) \emph{deliverable capacity} of the gas is the primary thermodynamic property of the material that determines the driving range~\cite{mason2014evaluating}. The adsorbed gas storage tank delivers the gaseous fuel to the engine via an (assumed) isothermal pressure swing \cite{sircar2002pressure}. The deliverable capacity (see Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set deliverable capacity targets for both adsorbed methane and hydrogen storage and delivery for vehicles. For methane, the Advanced Research Projects Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$ per L of adsorbent at 298 K using a 65\ bar to 5.8\ bar pressure swing \cite{simon2015materials}. For hydrogen, the DOE set a series of progressive targets at five year intervals, with the ultimate target of 0.05 kg H$_2$/L \cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a minimum of -40 $^\circ$C \cite{allendorf2018assessment}. Thus far, despite the emergence of highly tunable materials with enormous surface areas, such as metal-organic frameworks \cite{furukawa2013chemistry}, no porous material has met these deliverable capacity targets.

@@

G\'omez-Gualdr\'on \emph{et al.} \cite{gomez2017impact} introduced a model that accounted for gas-gas interactions via an intermolecular potential and idealized the substrate in two different ways: (1) discrete adsorption sites packed into an FCC lattice and (2) a volume endowed with a spatially uniform, background potential energy field. According to molecular simulation of methane adsorption, the ARPA-E deliverable capacity target of 315 L STP/L could be reached in both of these idealized substrates.
%The ARPA-E target of 315 L STP/L was reached when adsorption sites were endowed with an optimal heat of adsorption of 11.5 kJ/mol and adsorption sites were $5.3$ \AA~apart. In a second model, they endowed a volume with a background potential energy field, then simulated the adsorption of methane in the volume in the grand-canonical ensemble, using a Lennard-Jones potential for methane-methane interactions. The maximal deliverable capacity of 357 L STP/L was achieved with a background heat of adsorption of 8.6 kJ/mol. 
However, both models neglected the space occupied by atoms of the porous material that are needed to endow the adsorption sites/volume with the attractive potential energy. % To address this, in the third model, they constructed pseudo materials by placing Lennard-Jones spheres in space with tunable well depths. When constrained to form a connected network, none of the psuedo-materials reached the ARPA-E deliverable capacity target.

A third body of work attempted to account for both gas-gas interactions \emph{and} steric interactions of the gas with the atoms of the porous material.
% explores the upper limits of the deliverable capacity while accounting for gas-gas interactions \emph{and} the atoms of the porous material that are required to attract the guest; these material atoms exclude the adsorbate from regions of the control volume. 
%More works obtained an empirical upper bound on the deliverable capacity by explicitly accounting for the atoms of the material needed to create the potential energy field felt by the gas molecules.
Simulations of methane adsorption in hundreds of thousands of explicit nanoporous crystal structures---both real and hypothetical---suggested that the ARPA-E deliverable capacity target is infeasible \cite{simon2015materials}; the highest simulated methane deliverable capacity was 196 cm$^3$~STP/cm$^3$. Confidence in this conclusion rests upon (i) the accuracy of the intermolecular potentials describing the molecular interactions and (ii) the sufficient sampling of material space, i.e.\ that the structures considered are representative of the set of possible materials. To further explore material space and address sensitivity to the potentials used, scaling the Lennard-Jones potential well depths of material atoms to model enhanced interactions \cite{gomez2014exploring}, placing Lennard-Jones spheres in a unit cell randomly to form ``pseudo-materials'' \cite{kaija2018high}, and generating fictitious potential energy fields via a generative adversarial network trained on zeolite structures \cite{lee2019predicting} all generated model substrates that all failed to meet the ARPA-E methane deliverable capacity target.

@@

The first limitation of our proof is that we restricted ourselves to \emph{isothermal} pressure swing storage. By raising the temperature of the adsorbent during gas discharge to drive off residual gas \cite{gomez2014exploring}, the deliverable capacity could be enhanced, albeit at the cost of a more complicated engineering design of the fuel tank and vehicle.
%While this approach poses engineering challenges, in principle it could allow an arbitrarily large deliverable capacity.

@@

The second limitation of our proof arises in the assumption of a rigid substrate. The rigid substrate acts as a static potential energy field for gas molecules that is unchanged by the adsorption of gas.
% The second limitation of our proof arises in the assumption of a rigid substrate, which acts as a static potential energy field for gas molecules that is unchanged by the adsorption of gas.
For most porous materials this is a reasonable approximation, and this assumption is frequently made in both the simulation and theory of porous materials~\cite{witman2017influence}. However, there are cases where the substrate can in effect provide a very strongly gas-density-dependent interaction through structural flexibility~\cite{schneemann2014flexible}. A flagship example is MOF Co(bdp)~\cite{choi2008broadly}, which possesses a wine-rack-like topology capable of hinge motion. At low methane pressure, Co(bdp) adopts a collapsed, nonporous state, but expands to a porous state and fills with gas at higher pressures \cite{mason2015methane}. This allows Co(bdp) to fully expel its residual gas at low pressures.
Our upper bound does not consider such material effects and thus flexible materials could have significantly higher deliverable capacities.
% Such materials can indeed violate our upper bound and thus could lead to significantly improved deliverable capacities.

>>>>

% \jordan{I got the values from wikipedia but the citation that wikipedia gave didn't link to the correct paper? Article is Energy Density.
% THIS PAPER says H2 at 700 bar is 4.7 MJ/L: Review on processing of metal–organic framework (MOF) materials towards system integration for hydrogen storage
% }
At ambient conditions, both methane
%(0.036 MJ/L)
and hydrogen gas
%(0.01 MJ/L)
possess a very low volumetric energy density compared to (liquid) gasoline.
%(34.2 MJ/L)
Consequently, under storage space constraints in passenger vehicles, natural gas and hydrogen must be densified for onboard storage to achieve a reasonable driving range on a ``full'' tank of fuel. Traditional densification approaches are liquefaction (cryogenic storage near atmospheric pressure)
% (at 1 atm, liquid CH$_4$ at 111~K to achieve 22.2 MJ/L~\cite{makal2012methane}, liquid H$_2$ at 20 K to achieve 8~MJ/L \cite{suh2011hydrogen})
or compression to high pressures (room temperature storage).
% (200 bar for CH$_4$ to achieve 9.2 MJ/L \cite{makal2012methane} and 700 bar for H$_2$ to achieve 4.5-5.3 MJ/L~\cite{unknown}).
Both approaches require expensive infrastructure at refilling stations and significant energy input; e.g., liquefaction of hydrogen consumes at least 30\% of its energy content~\cite{bossel2003energy}. Moreover, high-pressure storage tanks are heavy, thick-walled, and non-conformable, while cryogenic storage tanks are bulky, expensive, and afflicted by boil-off losses~\cite{hasan2009minimizing}.
% \jordan{
% Both forms of densification suffer several drawbacks varying from safety issues,  excessively expensive, boil-off~\cite{hasan2009minimizing}, and extensive refilling infrastructure~\cite{bossel2003energy}. 
% }
% % Jordan: I commented this out! % Cory: I shorted it. I think it's important.

A promising approach to densify natural gas~\cite{makal2012methane,mason2014evaluating} and hydrogen~\cite{suh2011hydrogen,garcia2018benchmark} for vehicular storage is through physical adsorption in nanoporous materials at room temperature~\cite{schoedel2016role}. The internal surfaces of porous materials attract gas molecules through van der Waals, electrostatic, etc. interactions to achieve a higher adsorbed gas density than the bulk gas at the same temperature and pressure, allowing for room temperature and lower-pressure storage and alleviating many drawbacks of high-pressure storage.
% This would thereby reduce the cost of infrastructure at refilling stations, allow thinner-walled and therefore cheaper and lighter pressure vessels, reduce the energy requirements for gas densification, and alleviate safety concerns with high pressure storage.

@@

For a vehicle employing a porous material to store natural gas or hydrogen, the (volumetric) \emph{deliverable capacity} of the gas is the primary thermodynamic property of the material that determines the driving range~\cite{mason2014evaluating}. The adsorbed gas storage tank delivers the gaseous fuel to the engine via an (assumed) isothermal pressure swing~\cite{sircar2002pressure}. The deliverable capacity (see Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set deliverable capacity targets for both adsorbed methane and hydrogen storage and delivery for vehicles. For methane, the Advanced Research Projects Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$ per L of adsorbent at 298 K using a 65\ bar to 5.8\ bar pressure swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of progressive targets at five year intervals, with the ultimate target of 0.05 kg H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the emergence of highly tunable materials with enormous surface areas, such as metal-organic frameworks~\cite{furukawa2013chemistry}, no porous material has met these deliverable capacity targets.

@@

G\'omez-Gualdr\'on \emph{et al.}~\cite{gomez2017impact} introduced a model that accounted for gas-gas interactions via an intermolecular potential and idealized the substrate in two different ways: (1) discrete adsorption sites packed into an FCC lattice and (2) a volume endowed with a spatially uniform, background potential energy field. According to molecular simulation of methane adsorption, the ARPA-E deliverable capacity target of 315 L STP/L could be reached in both of these idealized substrates.
%The ARPA-E target of 315 L STP/L was reached when adsorption sites were endowed with an optimal heat of adsorption of 11.5 kJ/mol and adsorption sites were $5.3$ \AA~apart. In a second model, they endowed a volume with a background potential energy field, then simulated the adsorption of methane in the volume in the grand-canonical ensemble, using a Lennard-Jones potential for methane-methane interactions. The maximal deliverable capacity of 357 L STP/L was achieved with a background heat of adsorption of 8.6 kJ/mol. 
However, both models neglected the space occupied by atoms of the porous material that are needed to endow the adsorption sites/volume with the attractive potential energy. % To address this, in the third model, they constructed pseudo materials by placing Lennard-Jones spheres in space with tunable well depths. When constrained to form a connected network, none of the psuedo-materials reached the ARPA-E deliverable capacity target.

A third body of work attempted to account for both gas-gas interactions \emph{and} steric interactions of the gas with the atoms of the porous material.
% explores the upper limits of the deliverable capacity while accounting for gas-gas interactions \emph{and} the atoms of the porous material that are required to attract the guest; these material atoms exclude the adsorbate from regions of the control volume. 
%More works obtained an empirical upper bound on the deliverable capacity by explicitly accounting for the atoms of the material needed to create the potential energy field felt by the gas molecules.
Simulations of methane adsorption in hundreds of thousands of explicit nanoporous crystal structures---both real and hypothetical---suggested that the ARPA-E deliverable capacity target is infeasible~\cite{simon2015materials}; the highest simulated methane deliverable capacity was 196 cm$^3$~STP/cm$^3$. Confidence in this conclusion rests upon (i) the accuracy of the intermolecular potentials describing the molecular interactions and (ii) the sufficient sampling of material space, i.e.\ that the structures considered are representative of the set of possible materials. To further explore material space and address sensitivity to the potentials used, scaling the Lennard-Jones potential well depths of material atoms to model enhanced interactions~\cite{gomez2014exploring}, placing Lennard-Jones spheres in a unit cell randomly to form ``pseudo-materials''~\cite{kaija2018high}, and generating fictitious potential energy fields via a generative adversarial network trained on zeolite structures~\cite{lee2019predicting} all generated model substrates that all failed to meet the ARPA-E methane deliverable capacity target.

@@

The first limitation of our proof is that we restricted ourselves to \emph{isothermal} pressure swing storage. By raising the temperature of the adsorbent during gas discharge to drive off residual gas~\cite{gomez2014exploring}, the deliverable capacity could be enhanced, albeit at the cost of a more complicated engineering design of the fuel tank and vehicle.
%While this approach poses engineering challenges, in principle it could allow an arbitrarily large deliverable capacity.

@@

The second limitation of our proof arises in the assumption of a rigid substrate. The rigid substrate acts as a static potential energy field for gas molecules that is unchanged by the adsorption of gas.
% The second limitation of our proof arises in the assumption of a rigid substrate, which acts as a static potential energy field for gas molecules that is unchanged by the adsorption of gas.
For most porous materials this is a reasonable approximation, and this assumption is frequently made in both the simulation and theory of porous materials~\cite{witman2017influence}. However, there are cases where the substrate can in effect provide a very strongly gas-density-dependent interaction through structural flexibility~\cite{schneemann2014flexible}. A flagship example is MOF Co(bdp)~\cite{choi2008broadly}, which possesses a wine-rack-like topology capable of hinge motion. At low methane pressure, Co(bdp) adopts a collapsed, nonporous state, but expands to a porous state and fills with gas at higher pressures~\cite{mason2015methane}. This allows Co(bdp) to fully expel its residual gas at low pressures.
Our upper bound does not consider such material effects and thus flexible materials could have significantly higher deliverable capacities.
% Such materials can indeed violate our upper bound and thus could lead to significantly improved deliverable capacities.

### 2020-05-06 gas-adsorption/gas-ads.tex
made a number of ising edits and a thesis edit.
multiple changes to introduction and added citations to gas-ads abstract.

\begin{abstract}
  Due to their low volumetric energy density at ambient conditions, both hydrogen and natural gas are challenging to economically store onboard environmentally sustainable vehicles []. One strategy to densify these gases is to pack the fuel tank with a porous material [].
  Metal-organic frameworks are tunable, nanoporous materials with large internal surface areas and show considerable promise for densifying gases []. The US Department of Energy (DOE) has set volumetric deliverable capacity targets [] which, if met, would help to enable commercial adoption of hydrogen/natural gas as transportation fuels. Many have attempted to establish theoretical upper bounds on the deliverable capacity via pressure-swing adsorption using simplified models of the gas-substrate and gas-gas interaction []; none have established a rigorous upper bound on the deliverable capacity.
  Here, we present a theoretical upper bound on the deliverable capacity of a rigid material via an isothermal pressure-swing. % "pressure-swing storage doesn't make sense to me. storage and delivery  maybe but awk.
  % I added rigid since that could be important...
  To provide an extremum, we consider a substrate that provides a spatially uniform potential energy field for the gas. 
  \davidsays{Maybe we can add a phrase for an optimal uniform attraction?}
  Our bound is unique in that it directly relies on experimentally measured properties of the (real) bulk gas, without making approximations.
  We conclude that the goals set by the US DOE for natural gas and hydrogen storage are theoretically possible, but sufficiently close to the upper bound as to be impractical for any real porous material.
  % However, this upper bound directly leads to important realizations which should guide future development.
  However, limitations to the scope of applicability of our upper bound guide future material development efforts.
 % Firstly, one could extract the gas at a higher temperature than that used while filling [].
  Firstly, one could heat the adsorbent to drive off residual gas when the pressure diminishes [].
  Secondly, the fundamental physics of our upper bound do not pertain to
  % rule out
  any material that changes its structure in response to adsorbed gas, suggesting that flexible materials could still satisfy the DOE target [].
  % firstly, secondly vs first, second?
\end{abstract}

@@

\input{gas-ads-appendix.tex}

>>>>

\begin{abstract}
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard environmentally
sustainable vehicles~\cite{mason2014evaluating, sircar2002pressure}. One
strategy to densify these gases is to pack the fuel tank with a porous
material~\cite{?}. Metal-organic frameworks (MOFs) are tunable, nanoporous
materials with large internal surface areas and show considerable promise for
densifying gases~\cite{makal2012methane,mason2014evaluating,
suh2011hydrogen,garcia2018benchmark, schoedel2016role}. The US Department of
Energy (DOE) has set volumetric deliverable capacity targets~\cite{simon2015materials, h2targetsDOE} which, if met, would help to enable 
commercial adoption of hydrogen/natural gas as
transportation fuels. Many have attempted to establish theoretical upper bounds
on the deliverable capacity via pressure-swing adsorption using simplified
models of the gas-substrate and gas-gas interaction~\cite{gomez2014exploring, 
gomez2017impact, kaija2018high, lee2019predicting}; none have
established a rigorous upper bound on the deliverable capacity.
Here, we present a theoretical upper bound on the deliverable capacity of a
rigid material via an isothermal pressure-swing. To provide an extremum, we
consider a substrate that provides a spatially uniform potential energy field
for the gas. Our bound is unique in that it directly relies on experimentally
measured properties of the (real) bulk gas, without making approximations.
We conclude that the goals set by the US DOE for natural gas and hydrogen
storage are theoretically possible, but sufficiently close to the upper bound
as to be impractical for any real porous material. However, limitations to the
scope of applicability of our upper bound guide future material development 
efforts. Firstly, one could heat the adsorbent to drive off residual gas when
the pressure diminishes~\cite{gomez2014exploring}. Secondly, the fundamental
physics of our upper bound do not pertain to any material that changes its
structure in response to adsorbed gas, suggesting that flexible materials could
still satisfy the DOE targets~\cite{schneemann2014flexible, choi2008broadly, mason2015methane}.

%   Here, we present a theoretical upper bound on the deliverable capacity of a rigid material via an isothermal pressure-swing. % "pressure-swing storage doesn't make sense to me. storage and delivery  maybe but awk.
%   % I added rigid since that could be important...
%   To provide an extremum, we consider a substrate that provides a spatially uniform potential energy field for the gas. 
%   \davidsays{Maybe we can add a phrase for an optimal uniform attraction?}
%   Our bound is unique in that it directly relies on experimentally measured properties of the (real) bulk gas, without making approximations.
%   We conclude that the goals set by the US DOE for natural gas and hydrogen storage are theoretically possible, but sufficiently close to the upper bound as to be impractical for any real porous material.
%   % However, this upper bound directly leads to important realizations which should guide future development.
%   However, limitations to the scope of applicability of our upper bound guide future material development efforts.
%  % Firstly, one could extract the gas at a higher temperature than that used while filling [].
%   Firstly, one could heat the adsorbent to drive off residual gas when the pressure diminishes [].
%   Secondly, the fundamental physics of our upper bound do not pertain to
%   % rule out
%   any material that changes its structure in response to adsorbed gas, suggesting that flexible materials could still satisfy the DOE target [].
%   % firstly, secondly vs first, second?
\end{abstract}

@@

\appendix
\clearpage
\input{gas-ads-appendix.tex}

### 2020-05-06 thesis/chapter-1.tex
multiple changes to introduction and added citations to gas-ads abstract.

% This is part of the abstract of our paper.
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard environmentally
sustainable vehicles~\cite{?}. One strategy to densify these gases is to pack
the fuel tank with a porous material~\cite{?}. Metal-organic frameworks (MOFs)
are tunable, nanoporous materials with large internal surface areas and show
considerable promise for densifying gases~\cite{?}. The US Department of Energy
(DOE) has set volumetric deliverable capacity targets~\cite{?} which, if met,
would help to enable commercial adoption of hydrogen/natural gas as
transportation fuels. Many have attempted to establish theoretical upper bounds
on the deliverable capacity via pressure-swing adsorption using simplified
models of the gas-substrate and gas-gas interaction~\cite{?}; none have
established a rigorous upper bound on the deliverable capacity.

% This is part of the abstract(s) for APS Conferences.
Here, we present a theoretical upper bound on the deliverable capacity of a
rigid material via an isothermal pressure-swing. To provide an extremum, we
consider a substrate that provides a spatially uniform potential energy field
for the gas. Our bound is unique in that it directly relies on experimentally
measured properties of the (real) bulk gas, without making approximations.
We conclude that the goals set by the US DOE for natural gas and hydrogen
storage are theoretically possible, but sufficiently close to the upper bound
as to be impractical for any real porous material. However, limitations to the
scope of applicability of our upper bound guide future material development efforts. Firstly, one could heat the adsorbent to drive off residual gas when
the pressure diminishes~\cite{?}. Secondly, the fundamental physics of our
upper bound do not pertain to any material that changes its structure in
response to adsorbed gas, suggesting that flexible materials could still
satisfy the DOE targets~\cite{?}.

% Now add why a multidimensional 2D SAD would help and how we are working toward it.

\section{Summary}
We have provided the background necessary for understanding the various
flat-histogram methods and the various applied test systems. In the following
chapters, we detail our manuscripts and the method SAD applied to the various
physical test systems. We test SAD against a variety of other weight-based
flat-histogram methods on the square-well fluid, a Lennard-Jones cluster, and
the 2D Ising model. Each of these systems provides unique challenges to our
newly developed method SAD and convergence robustness is determined best by the
application to multiple systems.
% Now tie this in with gas adsorption.

>>>>

% This is part of the abstract of our paper.
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard environmentally
sustainable vehicles~\cite{mason2014evaluating, sircar2002pressure}. One
strategy to densify these gases is to pack the fuel tank with a porous
material~\cite{?}. Metal-organic frameworks (MOFs) are tunable, nanoporous
materials with large internal surface areas and show considerable promise for
densifying gases~\cite{makal2012methane,mason2014evaluating,
suh2011hydrogen,garcia2018benchmark, schoedel2016role}. The US Department of
Energy (DOE) has set volumetric deliverable capacity targets~\cite{simon2015materials, h2targetsDOE} which, if met, would help to enable 
commercial adoption of hydrogen/natural gas as
transportation fuels. Many have attempted to establish theoretical upper bounds
on the deliverable capacity via pressure-swing adsorption using simplified
models of the gas-substrate and gas-gas interaction~\cite{gomez2014exploring, 
gomez2017impact, kaija2018high, lee2019predicting}; none have
established a rigorous upper bound on the deliverable capacity.

Here, we present a theoretical upper bound on the deliverable capacity of a
rigid material via an isothermal pressure-swing. To provide an extremum, we
consider a substrate that provides a spatially uniform potential energy field
for the gas. Our bound is unique in that it directly relies on experimentally
measured properties of the (real) bulk gas, without making approximations.
We conclude that the goals set by the US DOE for natural gas and hydrogen
storage are theoretically possible, but sufficiently close to the upper bound
as to be impractical for any real porous material. However, limitations to the
scope of applicability of our upper bound guide future material development 
efforts. Firstly, one could heat the adsorbent to drive off residual gas when
the pressure diminishes~\cite{gomez2014exploring}. Secondly, the fundamental
physics of our upper bound do not pertain to any material that changes its
structure in response to adsorbed gas, suggesting that flexible materials could
still satisfy the DOE targets~\cite{schneemann2014flexible, choi2008broadly, mason2015methane}.

% Now add why a multidimensional 2D SAD would help and how we are working toward it.
Due to the difficulty in designing the ``ideal'' MOF for gas storage
applications, computational methods are necessary that can predict the
associated thermodynamic properties of interest. While SAD is an invaluable tool
for calculating a single isotherm (at a given density), an even more powerful
method is necessary for determining the best MOF for gas storage applications.
A multidimensional 2D SAD would allow researchers to compute all properties of
interest for all densities and temperatures. Our preliminary research has
yielded a robust method that has been tested on multiple systems and can be
extended into a 2D formulation.

\section{Summary}
We have provided the background necessary for understanding the various
flat-histogram methods and the various applied test systems. In the following
chapters, we detail our manuscripts and the method SAD applied to the various
physical test systems. We test SAD against a variety of other weight-based
flat-histogram methods on the square-well fluid, a Lennard-Jones cluster, and
the 2D Ising model. Each of these systems provides unique challenges to our
newly developed method SAD and convergence robustness is determined best by the
application to multiple systems.
% Now tie this in with gas adsorption.
We are currently working on two extensions which will enable a multidimensional
SAD. The first is adaptive interpolation histogram binning. This technique will
decrease the simulation time by orders of magnitude. The second is a version of
SAD that simulates ``number'' space rather than energy space. With the success
of these two extensions, we can begin the development of 2D SAD and thus provide
a powerful way for researchers to work toward enabling environmentally
sustainable light vehicle storage.
